---
title: 'M Carlin: Fourth Deliverable'
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r}
setwd("C:/Users/CarlinML/DACSS-690R/Fourth_Deliverable")
getwd()
```

# Open Clerkship Grades file from Third Deliverable
```{r}
ClerkshipGrades <- readRDS(gzcon(url("https://github.com/DACSS-690R/Third_Deliverable/raw/main/DataConcatenatedMerged/ClerkshipGrades.RDS")))
str(ClerkshipGrades) # 6427 rows
```

# Remove rows containing one or more missing values
```{r}
ClerkshipGrades_cleaned <- na.omit(ClerkshipGrades)
str(ClerkshipGrades_cleaned)
```

# Create new variable containing clerkship names, create new variable for academic year
```{r}
library(dplyr)
ClerkshipGrades_cleaned <- ClerkshipGrades_cleaned %>%
  mutate(Rotation = recode(Subject,
        "FC" = "Family Medicine Clerkship",
        "ME" = "Medicine Clerkship",
        "NU" = "Neurology Clerkship",
        "OB" = "Ob/Gyn Clerkship",
        "PE" = "Pediatric Clerkship",
        "PS" = "Psychiatry Clerkship",
        "SU" = "Surgery Clerkship"))

ClerkshipGrades_cleaned <- ClerkshipGrades_cleaned %>%
  mutate(AcadYear = recode(Term,
                "5202" = "AY22/23",
                "5300" = "AY22/23",
                "5301" = "AY22/23",
                "5302" = "AY23/24",
                "5400" = "AY23/24",
                "5401" = "AY23/24"))

ClerkshipGrades_cleaned$Final_Numeric <- as.numeric(ClerkshipGrades_cleaned$Final_Numeric)
ClerkshipGrades_cleaned$SPE_Numeric <- as.numeric(ClerkshipGrades_cleaned$SPE_Numeric)
ClerkshipGrades_cleaned$NBME_Numeric <- as.numeric(ClerkshipGrades_cleaned$NBME_Numeric)
```

# Aggregating with one group, one function, and one input variable
```{r}
FinalScoreAvgByClerkship=aggregate(data=ClerkshipGrades_cleaned,Final_Numeric~Rotation,mean)
FinalScoreAvgByClerkship
```

# Save output111 as RDS, CSV, and Parquet
```{r}
library(arrow)
saveRDS(FinalScoreAvgByClerkship, file = "finalOutput/output111.rds") 
write.csv(FinalScoreAvgByClerkship,"finalOutput/output111.csv")
arrow::write_parquet(FinalScoreAvgByClerkship,sink = "finalOutput/output111.parquet")


FinalScoreAvgByClerkship_rds <- readRDS("finalOutput/output111.rds")
FinalScoreAvgByClerkship_csv <- read.csv("finalOutput/output111.csv")
FinalScoreAvgByClerkship_parquet <- read_parquet("finalOutput/output111.parquet")
FinalScoreAvgByClerkship_rds
FinalScoreAvgByClerkship_csv
FinalScoreAvgByClerkship_parquet
```

# Aggregating with two groups, two functions, and one input variable
```{r}
FinalScoreAvgSDbyClerkshipYear=do.call(data.frame, aggregate(data=ClerkshipGrades_cleaned,Final_Numeric~Rotation + AcadYear,
          function(x) c(Mean = mean(x), SD = sd(x) ) ))
FinalScoreAvgSDbyClerkshipYear
```

# Save output221 as RDS, CSV, and Parquet
```{r}
saveRDS(FinalScoreAvgSDbyClerkshipYear, file = "finalOutput/output221.rds") 
write.csv(FinalScoreAvgSDbyClerkshipYear,"finalOutput/output221.csv")
arrow::write_parquet(FinalScoreAvgSDbyClerkshipYear,sink = "finalOutput/output221.parquet")


FinalScoreAvgSDbyClerkshipYear_rds <- readRDS("finalOutput/output221.rds")
FinalScoreAvgSDbyClerkshipYear_csv <- read.csv("finalOutput/output221.csv")
FinalScoreAvgSDbyClerkshipYear_parquet <- read_parquet("finalOutput/output221.parquet")
FinalScoreAvgSDbyClerkshipYear_rds
FinalScoreAvgSDbyClerkshipYear_csv
FinalScoreAvgSDbyClerkshipYear_parquet
```

# Aggregrating with one group, two input variables, and a different function for each
```{r}
SPEandNBMEbyClerkshipDiffFunc <- 
  ClerkshipGrades_cleaned |>
   group_by(Rotation) |>
   summarize(SPE_Mean = mean(SPE_Numeric),
            SPE_SD = sd(SPE_Numeric),
            NBME_Min = min(NBME_Numeric),
            NBME_Max = max(NBME_Numeric))
SPEandNBMEbyClerkshipDiffFunc
```

# Save output12f1f2 as RDS, CSV, and Parquet
```{r}
saveRDS(SPEandNBMEbyClerkshipDiffFunc, file = "finalOutput/output12f1f2.rds") 
write.csv(SPEandNBMEbyClerkshipDiffFunc,"finalOutput/output12f1f2.csv")
arrow::write_parquet(SPEandNBMEbyClerkshipDiffFunc,sink = "finalOutput/output12f1f2.parquet")

SPEandNBMEbyClerkshipDiffFunc_rds <- readRDS("finalOutput/output12f1f2.rds")
SPEandNBMEbyClerkshipDiffFunc_csv <- read.csv("finalOutput/output12f1f2.csv")
SPEandNBMEbyClerkshipDiffFunc_parquet <- read_parquet("finalOutput/output12f1f2.parquet")
SPEandNBMEbyClerkshipDiffFunc_rds
SPEandNBMEbyClerkshipDiffFunc_csv
SPEandNBMEbyClerkshipDiffFunc_parquet
```

